The imprint of global magma oceans on exoplanet demographics

### 2023-01-19 src/tex/ms.tex
add results section on FGK vs. M

\subsubsection{Spectral type of target stars}

@@

>>>>

\subsubsection{Spectral type of target stars}\label{sec:results_FGK_M}
Since receiving radiation is sensitive on the spectral type of the host star, the share of planets on either side of $S_\mathrm{thresh}$ is different for FGK and M~dwarfs.
We tested the detectability of the runaway greenhouse signal when only FGK or only M~dwarfs are considered (see Fig.~\ref{fig:plato_fgrid}).
The samples are volume and magnitude-limited ($d_\mathrm{max} = \SI{55}{\parsec}, M_\mathrm{G} < 11$), which makes the M~dwarf sample significantly larger with \var{N_M} planets compared to \var{N_FGK} planets in the FGK sample.
No significant detection is possible in the pure FGK sample, independent of the assumed geophysical parameters.
In the M~dwarf sample, the evidence threshold is reached around $f_\mathrm{rgh} \sim 0.5$, similar to the case above where all spectral types are considered.

@@

\begin{note}
    ...FGK vs. M...

To date, the majority of planets with radius measurements orbit FGK~dwarfs and lie in the runaway greenhouse regime.
    ...

    Our tests with different spectral types (Sect.~\ref{sec:results_FGK_M}) show that the information content of M~dwarfs in a sample dominates the hypothesis tests.
The reason is, besides their large number in a volume/magnitude-limited sample, that many detected M~dwarf planets are located near the threshold instellation.
As in the cases above, an M~dwarf survey profits from follow-up measurements of planetary masses with an order of magnitude increase in evidence.
\end{note}
